## ---------------------------
## Script name: RS_prediction_NCI60_V1.R
## Purpose of script: To test published signatures and compare to random 
## Author: Dr. John O'Connor
## Date Created: 09-09-2021
## Email: john.oconnor@qub.ac.uk
## ---------------------------
## Notes: 
## This script requires the cleaned data from the NCI60_cleaning_data.R script
## and random signatures from NCI60_random_siganture_testing_V1.R
## ---------------------------

##Load Packages##
```{r}
library(pls)
library(data.table)
library(reshape)
library(ggplot2)
library(Rfast)
library(caret)
library(infotheo)
library(e1071)
library(ggrepel)
library(ggpubr)
library(TOSTER)
```

#Data I/O
```{r}
homedir="C:/Users/HOMEDIRECTORY/"
Eschdata=read.table(paste(homedir,"Cleaned_data/Eschdata_NCI60.txt", sep=""))
Halldata=read.table(paste(homedir,"Cleaned_data/Halldata_NCI60.txt", sep=""))
dir.create(paste(homedir,"Fitted_models_NCI60/", sep=""))
dir.create(paste(homedir,"Equivalence_test_results/", sep=""))
modoutdir=paste(homedir,"Fitted_models_NCI60/", sep="")
sigdir=paste(homedir,"Signatures/",sep="")
genedatadir=paste(homedir,"Cleaned_data/NCI60_full_gene_averaged.txt", sep="")

##Setting parameters

#This will determine splitting of testing/training throughout
set.seed(1001)
dt=sample(nrow(Eschdata),nrow(Eschdata))

#Variance threshold for PCR regression 
varthres=80
```

##Functions
```{r}

c.fun<-function(df,center, scale) {
  return((df/scale)-center)
}

pca.fun<-function(train,test, varthres, sigsize, modprefix, modoutdir) {
  
  #Fit PCA
  pca_model=prcomp(train[,1:sigsize],scale =TRUE)
  
  #save(pca_model, file=paste(modoutdir,modprefix,"_PCA",".Rdata", sep=""))
  
  #Calculate cumulative variance explained by components
  pca.var=pca_model$sdev^2
  pervar=cumsum(round(pca.var/sum(pca.var)*100,1))
  
  #Find number of components to get closest to 80% explained
  if ((varthres-pervar[sum(pervar<varthres)])<((pervar[sum(pervar<varthres)+1])-varthres)){
    pccut=sum(pervar<varthres)} else {pccut=sum(pervar<varthres)+1}
  
  scores=data.frame(pca_model$x)
  scores$SF2=train$SF2

  #Fit linear regression with PCs as explanatory and AUC as response
  mod1=lm(as.formula(paste("SF2", "~",paste(colnames(scores)[c(1:pccut)], collapse = "+"),sep = "")),data = scores)
  
  #save(mod1, file=paste(modoutdir,modprefix,"_PCR",".Rdata", sep=""))
  
  ##Rotate, scale and centre test data
  newscores=data.frame(scale(test[,1:sigsize], pca_model$center, pca_model$scale) %*% pca_model$rotation)
  
  #Use PCA model for prediction and calculate accuracy
  pca_pred <- predict(mod1, newscores, ncomp = pccut)  
  output=list(pca_pred, abs(test$SF2-as.numeric(pca_pred)))
  
  return(output)
}
```

#Eschrich/RSI model testing
```{r}
#Convert to ranking of 10 genes
a=as.matrix(Eschdata[,1:10])
EschRank=data.frame(rowRanks(a))
EschRank$SF2=Eschdata$SF2
EschRank$site=Eschdata$site
colnames(EschRank)=colnames(Eschdata)
rownames(EschRank)=rownames(Eschdata)

sigsize_Esch=10
fold1=EschRank[dt[1:20],]
fold2=EschRank[dt[21:40],]
fold3=EschRank[dt[41:59],]

##Cross Validation 
##CV1
test=fold3
train=rbind(fold1, fold2)

#Prediction
pred1=-0.0098009*test[,1]+0.0128283*test[,2]+0.0254552*test[,3]-0.0017589*test[,4]-
  0.0038171*test[,5]+0.1070213*test[,6]-0.0002509*test[,7]-0.0092431*test[,8]-
  0.0204469*test[,9]-0.0441683*test[,10]

#Error
f1_ae=abs(test$SF2-as.numeric(pred1))
#save(mod1, file=paste(modoutdir,"ESCH_NCI60_mod1.Rdata", sep=""))

##CV2
test=fold2
train=rbind(fold1, fold3)

pred2=-0.0098009*test[,1]+0.0128283*test[,2]+0.0254552*test[,3]-0.0017589*test[,4]-
  0.0038171*test[,5]+0.1070213*test[,6]-0.0002509*test[,7]-0.0092431*test[,8]-
  0.0204469*test[,9]-0.0441683*test[,10]

f2_ae=abs(test$SF2-as.numeric(pred2))

#save(mod1, file=paste(modoutdir,"ESCH_NCI60_mod2.Rdata", sep=""))

##CV3
test=fold1
train=rbind(fold2, fold3)

pred3=-0.0098009*test[,1]+0.0128283*test[,2]+0.0254552*test[,3]-0.0017589*test[,4]-
  0.0038171*test[,5]+0.1070213*test[,6]-0.0002509*test[,7]-0.0092431*test[,8]-
  0.0204469*test[,9]-0.0441683*test[,10]

f3_ae=abs(test$SF2-as.numeric(pred3))

#save(mod1, file=paste(modoutdir,"ESCH_NCI60_mod3.Rdata", sep=""))

esch_ae=rbind(as.matrix(f1_ae),as.matrix(f2_ae),as.matrix(f3_ae))
esch_pred=rbind(as.matrix(pred1),as.matrix(pred2),as.matrix(pred3))
```
  
##Hall testing 
```{r}
sigsize=97

fold1=Halldata[dt[1:20],]
fold2=Halldata[dt[21:40],]
fold3=Halldata[dt[41:59],]

##CV1
test=fold3
train=rbind(fold1, fold2)

f1=pca.fun(train,test,varthres,sigsize, "HALL_HNSCC_NCI60_mod1", modoutdir)

##CV2
test=fold2
train=rbind(fold1, fold3)

f2=pca.fun(train,test,varthres,sigsize, "HALL_HNSCC_NCI60_mod2", modoutdir)

##CV3
test=fold1
train=rbind(fold2, fold3)

f3=pca.fun(train,test,varthres,sigsize,"HALL_HNSCC_NCI60_mod3", modoutdir)

hall_pred=rbind(as.matrix(f1[[1]]),as.matrix(f2[[1]]),as.matrix(f3[[1]]))
hall_ae=rbind(as.matrix(f1[[2]]),as.matrix(f2[[2]]),as.matrix(f3[[2]]))

pdata1=rbind(fold3[,98:99],fold2[,98:99],fold1[,98:99])
pdata1$esch_ae=esch_ae
pdata1$hall_ae=hall_ae

preddata=rbind(fold3[,98:99],fold2[,98:99],fold1[,98:99])
preddata$esch_pred=esch_pred
preddata$hall_pred=hall_pred
```

##Gene-Centric models 
```{r}
raw_datag=read.table(genedatadir)

genedirs=c(paste(sigdir,"Genes_Zhang.txt", sep=""),
           paste(sigdir,"Genes_Kim.txt", sep=""),
           paste(sigdir,"Genes_Amund_basal_do.txt", sep=""),
           paste(sigdir,"Genes_Amund_basal_SF2.txt",sep=""),
           paste(sigdir,"Genes_Tewari.txt", sep=""),
           paste(sigdir,"Genes_Reactome_Apop.txt", sep=""),
           paste(sigdir,"Genes_Reactome_Autophagy.txt", sep=""),
           paste(sigdir,"Genes_Reactome_cell_cycle_checkpoints.txt", sep=""),
           paste(sigdir,"Genes_Reactome_cell_cycle_chromosome_maintenance.txt", sep=""),
           paste(sigdir,"Genes_Reactome_cell_cycle_mitotic.txt", sep=""),
           paste(sigdir,"Genes_Reactome_DNA_repair.txt", sep=""),
           paste(sigdir,"Genes_Reactome_DNA_replication.txt", sep=""),
           paste(sigdir,"Genes_Reactome_Translation.txt", sep=""),
           paste(sigdir,"Genes_Venet.txt", sep=""))

modelnames=c("Eschrich", "Hall_HNSCC", "Zhang", "Kim", "Amund_D0", "Amund_SF2", "Tewari","R_Apop", "R_Auto", "R_Check", "R_Chrom", "R_Mitosis", "R_DNArepair", "R_DNAreplic", "R_Trans", "PCNAsig", "Intercept")

#fill with Eschrich and Hall now, in loop later
allsigsizes=c(10,97)

```

##Zhang model
```{r}
#Zhang model needs to use SVM and PLS

#Read Zhang gene data
x=read.table(genedirs[1],sep = "\n")

#Read gene names excluding SF2 and site (final 2 cols)
genenames=colnames(raw_datag)[1:(ncol(raw_datag)-2)]

#Match genes from Zhang to microarray data
m1=match(x[,], genenames)

#Count unmatched
sum(is.na(m1))
#List unmatched
x[which(is.na(m1)),1]
#Get matched
m2=m1[!is.na(m1)]

#Pull out matched gene data
reddata=cbind(raw_datag[,m2], raw_datag[,which(colnames(raw_datag)=="SF2"|colnames(raw_datag)=="site")])

#Add sig size to matrix
allsigsizes[3]=length(m2)

##Cross validation
fold1=reddata[dt[1:20],]
fold2=reddata[dt[21:40],]
fold3=reddata[dt[41:59],]

##CV1
test=fold3
train=rbind(fold1, fold2)

#Fit pls model on training data
pls_model=plsr(as.formula(paste("SF2", "~",paste(colnames(train)[c(1:129)], collapse = "+"),sep = "")),data = train,scale =TRUE, validation = "CV")
pls_scores=data.frame(pls_model$scores[,1:17])
pls_scores$SF2=train$SF2

#save(pls_model, file=paste(modoutdir,"ZHANG_NCI60_PLS_mod1.Rdata", sep=""))

form1=as.formula(paste("SF2", "~",paste(colnames(pls_scores[,1:17]), collapse = "+"),sep = ""))

obj <- tune(svm, form1, data = pls_scores,
            ranges = list(gamma = 2^(-10:3), cost = 2^(-10:7)))

mod_svm=obj$best.model
#save(mod_svm, file=paste(modoutdir,"ZHANG_NCI60_SVM_mod1.Rdata", sep=""))

#Get pls scores from test data and use SVM model to predict
#Center and scale test data
scaledtest=apply(test[,1:129], MARGIN=1, FUN=c.fun, pls_model$Xmeans, pls_model$scale)
newpcs=t(scaledtest) %*% pls_model$projection
newpcst=data.frame((newpcs)[,1:17])
pred1=predict(mod_svm, newpcst)
f1=abs(test$SF2-as.numeric(pred1))

##CV2
test=fold2
train=rbind(fold1, fold3)

#Fit pls model on training data
pls_model=plsr(as.formula(paste("SF2", "~",paste(colnames(train)[c(1:129)], collapse = "+"),sep = "")),data = train,scale =TRUE, validation = "CV")
#save(pls_model, file=paste(modoutdir,"ZHANG_NCI60_PLS_mod2.Rdata", sep=""))

pls_scores=data.frame(pls_model$scores[,1:17])
pls_scores$SF2=train$SF2

obj <- tune(svm, form1, data = pls_scores,
            ranges = list(gamma = 2^(-10:3), cost = 2^(-10:7)))
mod_svm=obj$best.model

#save(mod_svm, file=paste(modoutdir,"ZHANG_NCI60_SVM_mod2.Rdata", sep=""))

#Get pls scores from test data and use SVM model to predict
#Center and scale test data

scaledtest=apply(test[,1:129], MARGIN=1, FUN=c.fun, pls_model$Xmeans, pls_model$scale)
newpcs=t(scaledtest) %*% pls_model$projection
newpcst=data.frame((newpcs)[,1:17])
pred2=predict(mod_svm, newpcst)

f2=abs(test$SF2-as.numeric(pred2))

##CV3
test=fold1
train=rbind(fold2, fold3)

#Fit pls model on training data
pls_model=plsr(as.formula(paste("SF2", "~",paste(colnames(train)[c(1:129)], collapse = "+"),sep = "")),data = train,scale =TRUE, validation = "CV")
#save(pls_model, file=paste(modoutdir,"ZHANG_NCI60_PLS_mod3.Rdata", sep=""))

pls_scores=data.frame(pls_model$scores[,1:17])
pls_scores$SF2=train$SF2
pls_scores$metapcna=train$metapcna

obj <- tune(svm, form1, data = pls_scores,
            ranges = list(gamma = 2^(-10:3), cost = 2^(-10:7)))

mod_svm=obj$best.model
#save(mod_svm, file=paste(modoutdir,"ZHANG_NCI60_SVM_mod3.Rdata", sep=""))

#Get pls scores from test data and use SVM model to predict
#Center and scale test data
scaledtest=apply(test[,1:129], MARGIN=1, FUN=c.fun, pls_model$Xmeans, pls_model$scale)
newpcs=t(scaledtest) %*% pls_model$projection
newpcst=data.frame((newpcs)[,1:17])

pred3=predict(mod_svm, newpcst)
f3=abs(test$SF2-as.numeric(pred3))

zhang_pred=rbind(as.matrix(pred1),as.matrix(pred2),as.matrix(pred3))
zhang_ae=rbind(as.matrix(f1),as.matrix(f2),as.matrix(f3))

pdata1[,dim(pdata1)[2]+1]=zhang_ae
colnames(pdata1)[dim(pdata1)[2]]=paste(modelnames[3],"_ae",sep = "")

preddata[,dim(preddata)[2]+1]=zhang_pred
colnames(preddata)[dim(preddata)[2]]=paste(modelnames[3],"_pred",sep = "")
```

#Models using PCA approach 
```{r}
for (i in 2:length(genedirs)) {
  
  x=read.table(genedirs[i],sep = "\n")
  
  genenames=colnames(raw_datag)[1:(ncol(raw_datag)-2)]

  m1=match(x[,], genenames)
  
  sum(is.na(m1))
  x[which(is.na(m1)),1]
  m2=m1[!is.na(m1)]
  
  reddata=cbind(raw_datag[,m2], raw_datag[,which(colnames(raw_datag)=="SF2"|colnames(raw_datag)=="site")])
  
  fold1=reddata[dt[1:20],]
  fold2=reddata[dt[21:40],]
  fold3=reddata[dt[41:59],]
  
  sigsize=length(m2)
  allsigsizes[i+2]=sigsize
  
  ##CV1
  test=fold3
  train=rbind(fold1, fold2)
  
  label=paste(modelnames[i+2],"_NCI60_mod1", sep="")
  f1=pca.fun(train,test,varthres,sigsize,label, modoutdir)
  
  ##CV2
  test=fold2
  train=rbind(fold1, fold3)
  
  label=paste(modelnames[i+2],"_NCI60_mod2", sep="")
  f2=pca.fun(train,test,varthres,sigsize,label, modoutdir)
  
  ##CV3
  test=fold1
  train=rbind(fold2, fold3)
  
  label=paste(modelnames[i+2],"_NCI60_mod3", sep="")
  f3=pca.fun(train,test,varthres,sigsize,label, modoutdir)
  
  sig_pred=rbind(as.matrix(f1[[1]]),as.matrix(f2[[1]]),as.matrix(f3[[1]]))
  sig_ae=rbind(as.matrix(f1[[2]]),as.matrix(f2[[2]]),as.matrix(f3[[2]]))
  
  pdata1[,dim(pdata1)[2]+1]=sig_ae
  preddata[,dim(preddata)[2]+1]=sig_pred
  
  colnames(pdata1)[dim(pdata1)[2]]=paste(modelnames[i+2],"_ae",sep = "")
  colnames(preddata)[dim(preddata)[2]]=paste(modelnames[i+2],"_pred",sep = "")
  }

```

##Model with intercept only
```{r}
##Model with intercept only
##CV1
test=fold3
train=rbind(fold1, fold2)

mod=lm(SF2~1, data=train)
#save(mod, file=paste(modoutdir,"Intercept_NCI60_mod1.Rdata", sep=""))
pred1=predict(mod, test)
f1_ae=abs(test$SF2-as.numeric(pred1))

##CV2
test=fold2
train=rbind(fold1, fold3)

mod=lm(SF2~1, data=train)
#save(mod, file=paste(modoutdir,"Intercept_NCI60_mod2.Rdata", sep=""))
pred2=predict(mod, test)
f2_ae=abs(test$SF2-as.numeric(pred2))

##CV3
test=fold1
train=rbind(fold2, fold3)

mod=lm(SF2~1, data=train)
#save(mod, file=paste(modoutdir,"Intercept_NCI60_mod3.Rdata", sep=""))
pred3=predict(mod, test)
f3_ae=abs(test$SF2-as.numeric(pred3))

intercept_ae=rbind(as.matrix(f1_ae),as.matrix(f2_ae),as.matrix(f3_ae))
intercept_pred=rbind(as.matrix(pred1),as.matrix(pred2),as.matrix(pred3))

pdata1[,dim(pdata1)[2]+1]=intercept_ae
colnames(pdata1)[dim(pdata1)[2]]=paste("Intercept","_ae",sep = "")

preddata[,dim(preddata)[2]+1]=intercept_pred
colnames(preddata)[dim(preddata)[2]]=paste("Intercept","_pred",sep = "")
```

##Plotting results
```{r}
#Sites to factor variable
x=summary(factor(pdata1$site))
#Sites with more than 1 sample
x1=x[x>1]
tissues_acc=subset(pdata1[1:9], pdata1$site %in% names(x1))

#Reshaping and renaming variables
pdata2=reshape::melt(data = tissues_acc, id.vars = c("site"), measure.vars = colnames(pdata1)[3:9])

pdata2$site[pdata2$site == 'CNS'] <- 'CNS (n=6)'
pdata2$site[pdata2$site == 'Breast'] <- 'Breast (n=4)'
pdata2$site[pdata2$site == 'Blood'] <- 'Blood (n=6)'
pdata2$site[pdata2$site == 'Colon'] <- 'Colon (n=7)'
pdata2$site[pdata2$site == 'Kidney'] <- 'Kidney (n=8)'
pdata2$site[pdata2$site == 'Lung'] <- 'Lung (n=9)'
pdata2$site[pdata2$site == 'Ovary'] <- 'Ovary (n=7)'
pdata2$site[pdata2$site == 'Prostate'] <- 'Prostate (n=2)'
pdata2$site[pdata2$site == 'Skin'] <- 'Skin (n=10)'

#Model initials for plots
mshort=c("E", "H", "Z", "K", "AD", "AS", "T", "mP", "I")

##Tissue_specific
ggplot(pdata2, aes(x=variable, y=abs(value), colour=variable))+ facet_wrap(~site)+
  geom_boxplot()+ labs(title="",x="",y="MAE in prediction of SF2", color = "Model")+
  scale_color_discrete(labels = modelnames)+scale_x_discrete(labels= mshort)+
  theme(axis.text.x = element_text(size=6),axis.text.y = element_text(size=12),axis.title=element_text(size=14))+theme_bw()

```

#Tissue level means
```{r}
ag1=aggregate(pdata1[, 3:9], list(pdata1$site), mean)
ag2=aggregate(pdata1[, 3:9], list(pdata1$site), sd)

##Histogram SF2

pdata3=pdata1

pdata3$site[pdata3$site == 'CNS'] <- 'CNS (n=6)'
pdata3$site[pdata3$site == 'Breast'] <- 'Breast (n=4)'
pdata3$site[pdata3$site == 'Blood'] <- 'Blood (n=6)'
pdata3$site[pdata3$site == 'Colon'] <- 'Colon (n=7)'
pdata3$site[pdata3$site == 'Kidney'] <- 'Kidney (n=8)'
pdata3$site[pdata3$site == 'Lung'] <- 'Lung (n=9)'
pdata3$site[pdata3$site == 'Ovary'] <- 'Ovary (n=7)'
pdata3$site[pdata3$site == 'Prostate'] <- 'Prostate (n=2)'
pdata3$site[pdata3$site == 'Skin'] <- 'Skin (n=10)'

ggplot(pdata3, aes(x =SF2 , y = reorder(site,SF2, FUN = median))) + geom_boxplot()+theme_bw()+
  theme(axis.text.x = element_text(size=12),axis.text.y = element_text(size=12),axis.title=element_text(size=14))+
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +geom_vline(xintercept=median(pdata3$SF2), linetype="dashed", color = "red")+
  xlab("SF2")+ylab("Site")
```


#Plotting random signatures and models
```{r}

#Read median accuracy signatures absolute error
randsigs_ae=read.table(paste(homedir, "Random_signatures/NCI60/medsigsae.txt", sep=""))
sizes=c(10,19,31,49,97,114,127,129,131,146,168,182,272,289,306,546)

randsigs=data.frame(sizes)
randsigs$gmean=apply(randsigs_ae, 2, mean, na.rm = T)
randsigs$gsd=apply(randsigs_ae, 2, sd, na.rm = T)
randsigs$gdwn=randsigs$gmean-1.96*(randsigs$gsd/sqrt(dim(randsigs_ae)[1]))
randsigs$gup=randsigs$gmean+1.96*(randsigs$gsd/sqrt(dim(randsigs_ae)[1]))

pubsigs=data.frame(modelnames[1:length(modelnames)-1])
colnames(pubsigs)[1]="modelnames"
pubsigs$mean=apply(pdata1[,3:(length(pdata1)-1)], 2, mean, na.rm = T)
pubsigs$sd=apply(pdata1[,3:(length(pdata1)-1)], 2, sd, na.rm = T)
pubsigs$size=allsigsizes

ribbonsizes=randsigs$sizes
ribbonsizes[1]=ribbonsizes[1]-2
ribbonsizes[16]=ribbonsizes[16]+2

ggplot(pubsigs[1:7,])+geom_point(data=randsigs,aes(sizes,gmean), colour="red")+geom_line(data=randsigs,aes(sizes,gmean), colour="red")+geom_ribbon(data=randsigs,aes(x=ribbonsizes,y=gmean,ymin=gdwn, ymax=gup), alpha=0.1)+geom_text_repel(data=pubsigs,size=3,aes(x = size, y = mean, label = modelnames))+geom_point(data=pubsigs[1:7,],aes(size,mean), colour="black")+geom_point(data=pubsigs[8:16,],aes(size,mean),shape=1)+ylab("SF2 Mean Absolute Error")+xlab("Signature Size")+
  geom_hline(yintercept=mean(pdata1$Intercept_ae), linetype="dashed", color = "blue")+
  annotate(geom="text", x=400, y=0.183, label="Intercept only",color="blue")+
  annotate(geom="text", x=320, y=0.173, label="Median random signature",color="red")+
  scale_x_continuous(expand = c(0.026, 0))+theme_bw()+
  theme(axis.text.x = element_text(size=12),axis.text.y = element_text(size=12),axis.title=element_text(size=14))+
  theme(axis.line = element_line(colour = "black"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       panel.border = element_blank(),
       panel.background = element_blank())

```

#Tissue distance from overall mean and variation versus error
```{r}
#tissue mean, distance from overall mean
ag3=aggregate(pdata1[, 1], list(pdata1$site), mean)
ag3$x=ag3$x-mean(pdata1$SF2)

ax=cbind(ag1[,2:8], abs(ag3$x))

#Remove blood cell lines
ax2=ax[(2:9),]

d <- melt(ax2, id.vars="abs(ag3$x)")

colnames(d)[1]="SF2"
levels(d$variable)[levels(d$variable) == 'esch_ae'] <- "Eschrich"
levels(d$variable)[levels(d$variable) == 'hall_ae'] <- "Hall"
levels(d$variable)[levels(d$variable) == 'Zhang_ae'] <- "Zhang"
levels(d$variable)[levels(d$variable) == 'Kim_ae'] <- "Kim"
levels(d$variable)[levels(d$variable) == 'Amund_D0_ae'] <- "Amund_D0"
levels(d$variable)[levels(d$variable) == 'Amund_SF2_ae'] <- "Amund_SF2"
levels(d$variable)[levels(d$variable) == 'Tewari_ae'] <- "Tewari"

p1=ggplot(d, aes(SF2,value)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(cols=vars(variable))+coord_fixed(ratio = 2)+xlab(expression("Absolute (tissue-level SF2 - overall SF2)"))+
  ylab("SF2 Mean absolute error")+scale_x_continuous(breaks = c(0,0.2,0.4), limits = c(-0.02, 0.21))+theme(plot.margin = margin(0.2, 0.2, 0.2, 0.2, "cm"))

ag4=aggregate(pdata1[,1], list(pdata1$site), sd)
ax3=cbind(ag1[,2:8], ag4$x)
d2 <- melt(ax3, id.vars="ag4$x")

colnames(d2)[1]="SD"
levels(d2$variable)[levels(d2$variable) == 'esch_ae'] <- "Eschrich"
levels(d2$variable)[levels(d2$variable) == 'hall_ae'] <- "Hall"
levels(d2$variable)[levels(d2$variable) == 'Zhang_ae'] <- "Zhang"
levels(d2$variable)[levels(d2$variable) == 'Kim_ae'] <- "Kim"
levels(d2$variable)[levels(d2$variable) == 'Amund_D0_ae'] <- "Amund_D0"
levels(d2$variable)[levels(d2$variable) == 'Amund_SF2_ae'] <- "Amund_SF2"
levels(d2$variable)[levels(d2$variable) == 'Tewari_ae'] <- "Tewari"

p2=ggplot(d2, aes(SD,value)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(cols=vars(variable))+coord_fixed(ratio = 2)+xlab(expression("Tissue-level SF2 standard deviation"))+
  ylab("SF2 Mean absolute error")+scale_x_continuous(breaks = c(0,0.2), limits = c(0, 0.3))+theme(plot.margin = margin(0.2, 0.2, 0.2, 0.2, "cm"))

px=ggarrange(p1,p2, ncol=1)
```

#Equivalence tests against random signature
```{r}
bounds=c(-0.1, 0.1)
randsigs2=randsigs_ae
colnames(randsigs2)=c("r10","r19","r31","r49","r97","r114","r127","r129","r131","r146","r168","r182","r272","r289","r306","r546")
dat1=cbind(pdata1, randsigs2)

#Define pairs for comparison 
pairs1=list(c(i1="esch_ae",i2="r10"), 
           c(i1="hall_ae",i2="r97"), 
           c(i1="Zhang_ae",i2="r97"), 
           c(i1="Kim_ae",i2="r31"), 
           c(i1="Amund_D0_ae",i2="r19"), 
           c(i1="Amund_SF2_ae",i2="r168"), 
           c(i1="Tewari_ae",i2="r49"), 
           c(i1="R_Apop_ae",i2="r182"),
           c(i1="R_Auto_ae",i2="r146"), 
           c(i1="R_Check_ae",i2="r272"), 
           c(i1="R_Chrom_ae",i2="r114"), 
           c(i1="R_Mitosis_ae",i2="r546"), 
           c(i1="R_DNArepair_ae",i2="r306"), 
           c(i1="R_DNAreplic_ae",i2="r127"),
           c(i1="R_Trans_ae",i2="r289"), 
           c(i1="PCNAsig_ae",i2="r131"))

#TOST
x=dataTOSTpaired(data = dat1, pairs = pairs1, low_eqbound = -0.1,
high_eqbound = 0.1, alpha = 0.003, desc = TRUE, plots = TRUE, eqbound_type='raw')
x2=x$tost$asDF
x3=x$eqb$asDF 
x4=x$desc$asDF 
x2$diff=x4$"m[1]"-x4$"m[2]"
x2$cil=x3$"cil[raw]"
x2$ciu=x3$"ciu[raw]"
x2$i1=modelnames[1:16]
  
p10=ggplot(data=x2, aes(x=reorder(i1,diff), y=diff, colour=reorder(i1,diff)))+geom_point()+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+geom_hline(yintercept=c(-0.1,0.1), linetype="dashed", color = "black")+geom_errorbar(aes(ymin=cil,ymax=ciu,color=i1,width=0.2))+ylab("MAE difference from random signature of same size")+
  labs(color = "Signature")+annotate(geom="text", x=14, y=0.095, label="Upper bound",color="black")+annotate(geom="text", x=14, y=-0.095, label="Lower bound",color="black")

#write.table(x2,file=paste(homedir,"Equivalence_test_results/NCI60_equivalence_tests.csv", sep=""), sep=",")

```
